Lonely and online: an investigation of social media use and social isolation in China

### 2024-03-19 tandf/Social Isolation in China.qmd
First review pass done

More recent studies on the subject have found significantly more mixed and often negative evidence regarding the impact of social media on feelings of isolation. Primack et al. found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017]. A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies on social media's linkage to ill-being is negative [@valkenburg2022] while emphasizing the importance of heterogeneous effects. There are relatively fewer studies that consider all ages. However, those that have been conducted also emphasize that the relationship between social media use and well-being has possible negative effects but the effects seem to vary by personality type [@appel2020]. More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals; for some individuals, the effect may be quite negative for some while for others social media usage may have a modestly positive impact on well-being [@beyens2020; @ostic2021].

While most of the studies agree that the causal direction flows from social media use to feelings of isolation (though see [@nowland2018; @kim2017]), there is disagreement among authors about the specific mechanisms and causal pathways through which this relationship exists. For those who find a negative relationship between social media and well-being, one set of mechanisms suggests that the social media itself that is the problem. Cyberbullying, or more generally, repeated and aggressive online attacks against users has been systematically linked to feelings of social isolation [@ademiluyi2022]. Another proposed mechanism is upward comparisons of others - users observe content of friends or influencers who post luxurious or exotic experiences which cause users to encounter feelings of unhappiness or FOMO about their own life situation [@alabri2022; @büttner2022]. A third set of mechanisms primarily concern themselves with the physical changes that social media causes. Social media use has been shown to displace face to face activity, which leads to greater social isolation [@larson2018]. Heavy social media use also decreases hours of sleep, leading to greater feelings of anxiety and more social isolation [@twenge2017]. The current research suggests that which of these mechanisms is dominant depends on the age/demographic group in question and the societal context [@twenge2019].

@@

The case of China cannot resolve every debate in the literature or test all possible mechanisms but we do believe it can provide insight into a few of the more prominent proposed processes. Thus, given the existing literature and the context of China, we develop a series of testable hypotheses.

-   **H1a:** social media use should have a positive connection to social isolation due to strengthened government control over online content

-   **H1b:** social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.

-   **H2:** those who are able to use social media to make new friends will have lower social isolation scores than those who do not

-   **H3:** the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation

>>>>

More recent studies on the subject have found significantly more mixed and often negative evidence regarding the impact of social media on feelings of isolation. Primack et al. found a negative relationship between social media use and social isolation in youth in a representative sample [@primack2017]. A meta-review of the literature on adolescent social media usage notes that while the effect size is often small the relationship in most studies on social media's linkage to ill-being is negative [@valkenburg2022] while emphasizing the importance of heterogeneous effects. There are relatively fewer studies that consider all ages. However, those that have been conducted also emphasize that the relationship between social media use and well-being has possible negative effects but the effects seem to vary by personality type [@appel2020]. More recent research has reinforced the finding that the effect of social media on measures like social isolation may be highly heterogeneous across individuals; for some individuals, the effect may be quite negative for some while for others social media usage may have a modestly positive impact on well-being [@beyens2020; @ostic2021]. For example, for some users moderate social media use may have no significant impact but for those who suffer from social media addiction, the effect can be highly negative [@alhassan2018; @aljomaa2016] (though see [@al-kandari2021; @chen2017] for more complex findings).

While most of the studies agree that the causal direction flows from social media use to feelings of isolation (though see [@nowland2018; @kim2017]), there is disagreement among authors about the specific mechanisms and causal pathways through which this relationship exists. For those who find a negative relationship between social media and well-being, one set of mechanisms suggests that the social media itself that is the problem. Cyberbullying, or more generally, repeated and aggressive online attacks against users has been systematically linked to feelings of social isolation [@ademiluyi2022]. Another proposed mechanism is upward comparisons of others - users observe content of friends or influencers who post luxurious or exotic experiences which cause users to encounter feelings of unhappiness or FOMO about their own life situation [@alabri2022; @büttner2022]. A third set of mechanisms primarily concern themselves with the physical changes that social media causes. Social media use has been shown to displace face to face activity, which leads to greater social isolation [@larson2018]. The current research suggests that which of these mechanisms is dominant depends on the age/demographic group in question and the societal context [@twenge2019].

@@

The case of China cannot resolve every debate in the literature or test all possible mechanisms but we do believe it can provide insight into a few of the more prominent proposed processes. Thus, given the existing literature and the context of China, we develop a series of testable hypotheses that shed light on our research question.

-   **H$1_a$**: social media use should have a positive connection to social isolation due to strengthened government control over online content

-   **H$1_b$**: social media use should have a negative connection to social isolation due to the dominance of influencer culture in China, moderated by age.

-   **H$2$**: those who are able to use social media to make new friends will have lower social isolation scores than those who do not

-   **H$3$:** the urban/rural divide will produce differential impacts in the above hypotheses on the relationship between social media use and social isolation

### 2024-03-19 tandf/Social-Isolation-in-China.tex
First review pass done

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

Research is quite mixed when it comes to identifying the relationship
between social media use and feelings of isolationism. Early research
suggested that the internet would build social capital, or an
interconnectedness between people, and that social media platforms were
the ultimate way to bring people together. Since then, research on the
subject has been decidedly more mixed. On one hand, some authors have
found social media may encourage social isolation, and ultimately,
social media users may feel more disconnected from others than those who
do not use social media. On the other hand, others have found that there
is only a minimal relationship between these two variables. More recent
scholarship has suggested that social media use may produce
heterogeneous effects on individuals' sense of well-being. This study
uses the little-studied Chinese social media environment to try and gain
leverage on this question - the Chinese online environment has certain
features that should both moderate and exacerbate key causal pathways
previously identified in the literature. To resolve these debates, we
employ a large survey (n=2292) of Chinese internet users and test a
variety of regression specifications.\footnote{All data and analysis
  files for this research are available at the author's website.} The
main result is that social media use is generally negatively related to
social isolation, though the nature of this relationship changes
depending on the urbanicity of the respondent - being in a rural area
amplifies this relationship. This finding lends support both to the
previous negative relationship findings and also reinforce the findings
that emphasize heterogeneous effects.

@@

More recent studies on the subject have found significantly more mixed
and often negative evidence regarding the impact of social media on
feelings of isolation. Primack et al.~found a negative relationship
between social media use and social isolation in youth in a
representative sample (Primack et al., 2017). A meta-review of the
literature on adolescent social media usage notes that while the effect
size is often small the relationship in most studies on social media's
linkage to ill-being is negative (Valkenburg et al., 2022) while
emphasizing the importance of heterogeneous effects. There are
relatively fewer studies that consider all ages. However, those that
have been conducted also emphasize that the relationship between social
media use and well-being has possible negative effects but the effects
seem to vary by personality type (Appel et al., 2020). More recent
research has reinforced the finding that the effect of social media on
measures like social isolation may be highly heterogeneous across
individuals; for some individuals, the effect may be quite negative for
some while for others social media usage may have a modestly positive
impact on well-being (Beyens et al., 2020; Ostic et al., 2021).

While most of the studies agree that the causal direction flows from
social media use to feelings of isolation (though see (Kim, 2017;
Nowland et al., 2018)), there is disagreement among authors about the
specific mechanisms and causal pathways through which this relationship
exists. For those who find a negative relationship between social media
and well-being, one set of mechanisms suggests that the social media
itself that is the problem. Cyberbullying, or more generally, repeated
and aggressive online attacks against users has been systematically
linked to feelings of social isolation (Ademiluyi et al., 2022). Another
proposed mechanism is upward comparisons of others and the weak nature
of online connections - both of these have been found to generate social
anxiety and social isolation (Alabri, 2022; Büttner \& Rudert, 2022). A
third set of mechanisms primarily concern themselves with the physical
changes that social media causes. Social media use has been shown to
displace face to face activity, which leads to greater social isolation
(Larson et al., 2018). Heavy social media use also decreases hours of
sleep, leading to greater feelings of anxiety and more social isolation
(Twenge et al., 2017). The current research suggests that which of these
mechanisms is dominant depends on the age/demographic group in question
and the societal context (Twenge, 2019).

Most of the existing research on the subject focuses on Western highly
developed societies, and this focus may limit variation on key
independent variables given the similar social and institutional context
in which users are embedded. In particular, we believe the case of China
can provide leverage in three areas that existing theories have
difficulty resolving. The first is that

To address this problem, this study aims to understand how these complex
dynamics interact in the non-Western setting of China. Relatively little
is known about China's level of social isolation, though what evidence
that does exist suggests that it is on the rise. Twenge et al.'s study
found that adolescent feelings of loneliness have generally been on the
rise in comparable East Asian countries (Twenge et al., 2021). News
reports have highlighted the increasing number of people who consider
themselves to be online outcasts or losers (\emph{diaosi})
(\emph{China{'}s Latest Social Media Trend}, 2016; Nan, 2013;
Szablewicz, 2014). We do not aim to make a direct comparison between
China and Western countries but rather highlight the way in which
China's unique context helps shed light on which contextual factors
matter in understanding the linkage between the two variables.

The most important of these contextual factor in China is that social
media space that is highly controlled online environment. Many people
are aware that the Chinese government heavily censors politically
sensitive content on online platforms. Fewer are aware that the Chinese
government spends as much, if not more, effort to clean up non-political
negative or distressing content on the Chinese internet, such as scams,
instances of cyber bullying, disturbing videos, and vulgar content
(Wang, 2020). This control impulse also extends content the government
views as spiritually polluting, such as pornography, scantily dressed
women, and other escapist content. While the Chinese government and
online platforms are not 100 per cent effective in their ability to
completely stamp out such content, the default is that such content is
actively restricted, while US platforms tent to take a more pro-speech
regulatory position (J. Liu \& Yang, 2022). If one of the main
mechanisms through which social media promotes social isolation occurs
is exposure to negative content, then this highly regulated online
environment should lead to a weaker relationship between social media
use and isolation. Suggestive of this is a study by Liu and Liu that
finds Chinese who consumed more commercialized and sensationalized media
reported more trauma during the first COVID-19 outbreak in China than
those who followed government sources (C. Liu \& Liu, 2020).

On the other hand, China also has a highly robust online influencer
culture. While social media influencers are a global phenomena, China
has perhaps the most commercialized version of influencing. Social media
influencers are developed by large agencies and work in an almost
assembly-line fashion to promote products on livestreams or pitch
sponsored products. In this influencer culture, less attention is paid
to authenticity and personality and relatively more emphasis is placed
on consumerism, brand promotion, and image (Tam, 2019; Wei, 2023). Given
that previous research has suggested one of the main channels through
which social media creates feelings of isolation is negative personal
comparisons with online content (so-called ``FOMO'' - fear of missing
out), heavy social media use may increase the strength of the
relationship between social media use and social isolation through
consumption of such highly commercialized content. These influencers are
most popular among young consumers so one may expect that only younger
users would experience these effects.

Additionally, China's social media environment is relatively unique in
that the dominant messaging platform is also the largest social media
app (WeChat). Users can use it simply to chat with family and friends,
they can use it to post photos and other content about their life in a
feed that works similarly to Facebook, or they can browse videos of
others in a method similar to Tiktok. Previous research has indicated
that while, on the whole, social media increases social isolation, for
users that primarily use it to contact friends and family, its use can
counteract the negative effects (Hajek \& König, 2019; Lim et al.,
2020). In this way, those that heavily use these type of combined
platforms may engage in multiple uses of social media that tend to
cancel each other out. Given the ubiquity of WeChat in China, such a
relationship seems plausible.

Finally, the nexus of social isolation and social media use in China has
played out in the context of one of the most rapid periods of
urbanization in human history. Hundreds of millions of people have
shifted from rural subsistence farming to participating in an urban
market economy. The existing literature finds that urbanicity is an
important factor in levels and mechanisms for social isolation; many
studies of Western societies have found that rural residents, while
having stronger familial bonds, also can more easily experience social
isolation without those bonds (Henning-Smith et al., 2018; Kaye, 2017;
Koning et al., 2017). In China, less is known about the differential
effects of the urban rural divide on feelings of social isolation but
the research that does exist suggests that urban environments can be
especially isolating, particularly for rural to urban migrants
particularly due to lack of access to traditional support systems and
familial connections (Li \& Rose, 2017).

Given the existing literature and the context of China, this leads to a
series of testable hypotheses.

\begin{itemize}
\item
  \textbf{H1a:} social media use should have a positive connection to
  social isolation due to strengthened government control over online
  content
\item
  \textbf{H1b:} social media use should have a negative connection to
  social isolation due to the dominance of influencer culture in China,
  moderated by age.
\item
  \textbf{H2:} those who are able to use social media to make new
  friends will have lower social isolation scores than those who do not
\item
  \textbf{H3:} the urban/rural divide will produce differential impacts
  in the above hypotheses on the relationship between social media use
  and social isolation
\end{itemize}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-chinas2016}{}}%
\emph{China{'}s latest social media trend: Diaosi / loser subculture}.
(2016).
\url{https://www.appnova.com/chinas-latest-social-media-trend-diaosi-loser-subculture/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-hajek2019}{}}%
Hajek, A., \& König, H.-H. (2019). The association between use of online
social networks sites and perceived social isolation among individuals
in the second half of life: results based on a nationally representative
sample in Germany. \emph{BMC Public Health}, \emph{19}(1), 40.
\url{https://doi.org/10.1186/s12889-018-6369-6}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-li2017}{}}%
Li, J., \& Rose, N. (2017). Urban social exclusion and mental health of
China's rural-urban migrants {\textendash} A review and call for
research. \emph{Health \& Place}, \emph{48}, 20--30.
\url{https://doi.org/10.1016/j.healthplace.2017.08.009}

\leavevmode\vadjust pre{\hypertarget{ref-lim2020}{}}%
Lim, M. H., Eres, R., \& Vasan, S. (2020). Understanding loneliness in
the twenty-first century: An update on correlates, risk factors, and
potential solutions. \emph{Social Psychiatry and Psychiatric
Epidemiology}, \emph{55}(7), 793--810.
\url{https://doi.org/10.1007/s00127-020-01889-7}

\leavevmode\vadjust pre{\hypertarget{ref-liu2020}{}}%
Liu, C., \& Liu, Y. (2020). Media Exposure and Anxiety during COVID-19:
The Mediation Effect of Media Vicarious Traumatization.
\emph{International Journal of Environmental Research and Public
Health}, \emph{17}(13), 4720.
\url{https://doi.org/10.3390/ijerph17134720}

\leavevmode\vadjust pre{\hypertarget{ref-liu2022}{}}%
Liu, J., \& Yang, L. (2022). {``}Dual-Track{''} platform governance on
content: A comparative study between China and United States.
\emph{Policy \& Internet}, \emph{14}(2), 304--323.
\url{https://doi.org/10.1002/poi3.307}

\leavevmode\vadjust pre{\hypertarget{ref-nan2013}{}}%
Nan, W. (2013). China's underdog youth find success in 'diaosi' - or
'loser' - identity. \emph{South China Morning Post}.
\url{https://www.scmp.com/news/china/article/1232976/chinas-underdog-youth-find-success-diaosi-or-loser-identity}

@@

\leavevmode\vadjust pre{\hypertarget{ref-szablewicz2014}{}}%
Szablewicz, M. (2014). The {`}losers{'} of China{'}s Internet: Memes as
{`}structures of feeling{'} for disillusioned young netizens.
\emph{China Information}, \emph{28}(2), 259--275.
\url{https://doi.org/10.1177/0920203X14531538}

@@

\leavevmode\vadjust pre{\hypertarget{ref-twenge2021}{}}%
Twenge, J. M., Haidt, J., Blake, A. B., McAllister, C., Lemon, H., \& Le
Roy, A. (2021). Worldwide increases in adolescent loneliness.
\emph{Journal of Adolescence}, \emph{93}, 257--269.
\url{https://doi.org/10.1016/j.adolescence.2021.06.006}

\leavevmode\vadjust pre{\hypertarget{ref-twenge2017}{}}%
Twenge, J. M., Krizan, Z., \& Hisler, G. (2017). Decreases in
self-reported sleep duration among U.S. adolescents
2009{\textendash}2015 and association with new media screen time.
\emph{Sleep Medicine}, \emph{39}, 47--53.
\url{https://doi.org/10.1016/j.sleep.2017.08.013}

@@

>>>>

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable, sharp corners, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Research is quite mixed when it comes to identifying the relationship
between social media use and feelings of isolationism. Early research
suggested that the internet would build social capital, or an
interconnectedness between people, and that social media platforms were
the ultimate way to bring people together (Ellison et al., 2007). Since
then, research on the subject has been decidedly more mixed (Duradoni et
al., 2020; Jiménez et al., 2022; Valkenburg et al., 2022). On one hand,
some authors have found social media may encourage social isolation, and
ultimately, social media users may feel more disconnected from others
than those who do not use social media. On the other hand, others have
found that there is only a minimal relationship between these two
variables. More recent scholarship has suggested that social media use
may produce heterogeneous effects on individuals' sense of well-being
(Ivie et al., 2020; Ostic et al., 2021).

This study uses the little-studied Chinese social media environment to
answer two research questions that remain unresolved in the literature:
1) through which channels or mechanisms do possible heterogeneous
effects operate through and 2) how much does internet context change the
relationship between social isolation and social media use. The reason
that we believe the case of China can be helpful in answering these
question is that Chinese online environment has certain features that
should both moderate and exacerbate key causal pathways previously
identified in the literature. To resolve these debates, we employ a
large survey (n=2292) of Chinese internet users and test a variety of
regression specifications.\footnote{All data and analysis files for this
  research are available at the author's website.} The main result is
that social media use is generally negatively related to social
isolation, though the nature of this relationship changes depending on
the urbanicity of the respondent - being in a rural area amplifies this
relationship. These results are consistent with a mechanism that links
the two via the harmfulness of being exposed to constant online
comparisons (so-called FOMO or fear of missing out). However, the
contextual differences of the Chinese internet compared to the Western
intern do not appear to significantly alter the relationship.

@@

More recent studies on the subject have found significantly more mixed
and often negative evidence regarding the impact of social media on
feelings of isolation. Primack et al.~found a negative relationship
between social media use and social isolation in youth in a
representative sample (Primack et al., 2017). A meta-review of the
literature on adolescent social media usage notes that while the effect
size is often small the relationship in most studies on social media's
linkage to ill-being is negative (Valkenburg et al., 2022) while
emphasizing the importance of heterogeneous effects. There are
relatively fewer studies that consider all ages. However, those that
have been conducted also emphasize that the relationship between social
media use and well-being has possible negative effects but the effects
seem to vary by personality type (Appel et al., 2020). More recent
research has reinforced the finding that the effect of social media on
measures like social isolation may be highly heterogeneous across
individuals; for some individuals, the effect may be quite negative for
some while for others social media usage may have a modestly positive
impact on well-being (Beyens et al., 2020; Ostic et al., 2021). For
example, for some users moderate social media use may have no
significant impact but for those who suffer from social media addiction,
the effect can be highly negative (Alhassan et al., 2018; Aljomaa et
al., 2016) (though see (Al-Kandari \& Al-Sejari, 2021; Chen et al.,
2017) for more complex findings).

While most of the studies agree that the causal direction flows from
social media use to feelings of isolation (though see (Kim, 2017;
Nowland et al., 2018)), there is disagreement among authors about the
specific mechanisms and causal pathways through which this relationship
exists. For those who find a negative relationship between social media
and well-being, one set of mechanisms suggests that the social media
itself that is the problem. Cyberbullying, or more generally, repeated
and aggressive online attacks against users has been systematically
linked to feelings of social isolation (Ademiluyi et al., 2022). Another
proposed mechanism is upward comparisons of others - users observe
content of friends or influencers who post luxurious or exotic
experiences which cause users to encounter feelings of unhappiness or
FOMO about their own life situation (Alabri, 2022; Büttner \& Rudert,
2022). A third set of mechanisms primarily concern themselves with the
physical changes that social media causes. Social media use has been
shown to displace face to face activity, which leads to greater social
isolation (Larson et al., 2018). The current research suggests that
which of these mechanisms is dominant depends on the age/demographic
group in question and the societal context (Twenge, 2019).

Most of the existing research on the subject focuses on Western highly
developed societies, and this focus limits variation on key independent
variables given the similar social and institutional context in which
users are embedded. To address this problem, this study aims to
understand how these complex dynamics interact in the non-Western
setting of China. We believe the setting of China gives additional
leverage to investigate issues of heterogeneity and the importance of
context for several reasons. Firstly, the highly controlled nature of
China's internet space prevents user exposure to some of the more
threatening online content (such as cyberbullying) that is hypothesized
to be a factor in creating a negative relationship between social media
and feelings of social isolation (Wang, 2020). If this mechanism were
the dominant reason for previous findings of a negative relationship
between the two, one would expect the relationship to be more positive
in China. Relatedly, China has a more commercial and robust influencer
culture that often dominates user's social media consumption (Tam, 2019;
Wei, 2023). If the main pathway creating a negative relationship is via
user's comparisons of their lives with others (FOMO), we expect the
relationship between social media use and feelings of social isolation
to be greater in China.

Finally, China has undergone a period of very rapid urbanization in the
last 40 years, a development that has brought about enormous changes to
traditional social structures (Xu \& Xia, 2014). This rapid urbanization
can help test two important unresolved questions in the existing
literature that are difficult to resolve given that urbanization in
Western countries is a process that largely finished by the advent of
social media. The first is whether social media can provide a means to
decrease social isolation among those who actively seek it out to make
friends. China's rapid urbanization and attendant human migration has
created a large population of people that lack strong social bonds and
may use social media as a method to create new social bonds (as the
earlier theorists of social media hypothesized users may employ the
technology). The existing literature on the West finds that urbanicity
is an important factor in levels and mechanisms for social isolation;
many studies of Western societies have found that rural residents, while
having stronger familial bonds, also can more easily experience social
isolation without those bonds (Henning-Smith et al., 2018; Kaye, 2017;
Koning et al., 2017). Social media use in China could therefore either
help mitigate the feelings of isolation brought on by rapid urbanization
by connecting family members who have left the countryside for urban
work (based on the earlier, more positive views of social media's
potential) or amplify further the feelings of isolation due to several
of the proposed negative relationship mechanisms.

The case of China cannot resolve every debate in the literature or test
all possible mechanisms but we do believe it can provide insight into a
few of the more prominent proposed processes. Thus, given the existing
literature and the context of China, we develop a series of testable
hypotheses that shed light on our research question.

\begin{itemize}
\item
  \textbf{H\(1_a\)}: social media use should have a positive connection
  to social isolation due to strengthened government control over online
  content
\item
  \textbf{H\(1_b\)}: social media use should have a negative connection
  to social isolation due to the dominance of influencer culture in
  China, moderated by age.
\item
  \textbf{H\(2\)}: those who are able to use social media to make new
  friends will have lower social isolation scores than those who do not
\item
  \textbf{H\(3\):} the urban/rural divide will produce differential
  impacts in the above hypotheses on the relationship between social
  media use and social isolation
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-alhassan2018}{}}%
Alhassan, A. A., Alqadhib, E. M., Taha, N. W., Alahmari, R. A., Salam,
M., \& Almutairi, A. F. (2018). The relationship between addiction to
smartphone usage and depression among adults: a cross sectional study.
\emph{BMC Psychiatry}, \emph{18}(1), 1--8.
\url{https://doi.org/10.1186/s12888-018-1745-4}

\leavevmode\vadjust pre{\hypertarget{ref-aljomaa2016}{}}%
Aljomaa, S. S., Al.Qudah, M. F., Albursan, I. S., Bakhiet, S. F., \&
Abduljabbar, A. S. (2016). Smartphone addiction among university
students in the light of some variables. \emph{Computers in Human
Behavior}, \emph{61}, 155--164.
\url{https://doi.org/10.1016/j.chb.2016.03.041}

\leavevmode\vadjust pre{\hypertarget{ref-al-kandari2021}{}}%
Al-Kandari, Y. Y., \& Al-Sejari, M. M. (2021). Social isolation, social
support and their relationship with smartphone addiction.
\emph{Information, Communication \& Society}, \emph{24}(13), 1925--1943.
\url{https://doi.org/10.1080/1369118X.2020.1749698}

@@

\leavevmode\vadjust pre{\hypertarget{ref-chen2017}{}}%
Chen, C., Zhang, K. Z. K., Gong, X., Zhao, S. J., Lee, M. K. O., \&
Liang, L. (2017). Examining the effects of motives and gender
differences on smartphone addiction. \emph{Computers in Human Behavior},
\emph{75}, 891--902. \url{https://doi.org/10.1016/j.chb.2017.07.002}

\leavevmode\vadjust pre{\hypertarget{ref-duradoni2020}{}}%
Duradoni, M., Innocenti, F., \& Guazzini, A. (2020). Well-Being and
Social Media: A Systematic Review of Bergen Addiction Scales.
\emph{Future Internet}, \emph{12}(2), 24.
\url{https://doi.org/10.3390/fi12020024}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-ivie2020}{}}%
Ivie, E. J., Pettitt, A., Moses, L. J., \& Allen, N. B. (2020). A
meta-analysis of the association between adolescent social media use and
depressive symptoms. \emph{Journal of Affective Disorders}, \emph{275},
165--174. \url{https://doi.org/10.1016/j.jad.2020.06.014}

\leavevmode\vadjust pre{\hypertarget{ref-jimuxe9nez2022}{}}%
Jiménez, A. C., Vaillancourt, M., Zhu, P., \& Seon, Q. (2022). Social
Media and Mental Health: What We Know. \emph{McGill Journal of
Medicine}, \emph{20}(2). \url{https://doi.org/10.26443/mjm.v20i2.852}

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-xu2014}{}}%
Xu, A., \& Xia, Y. (2014). The changes in mainland chinese families
during the social transition: A critical analysis. \emph{Journal of
Comparative Family Studies}, \emph{45}(1), 31--53.
\url{https://doi.org/10.3138/jcfs.45.1.31}
